---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Greatrex.Functions

The goal of Greatrex.Functions is to collate functions I find useful or that underpin many of my scripts. These might be tiny things from stack overflow answers, little ways to make coding easier, or weird custom functions that only get used by me in specific ways

## Installation

You can install the development version of Greatrex.Functions like so:

```{r,eval=FALSE}
 #install.packages(remotes)  # As needed
 remotes::install_github('hgreatrex/Greatrex.Functions',force=TRUE)
```

## What functions are there?

Let's just list them for now. More to come

```{r example}
library(Greatrex.Functions)
ls("package:Greatrex.Functions")
```



```{r, include=FALSE,eval=FALSE}
#You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. 
# `devtools::build_readme()` is handy for this. 
#You could also use GitHub Actions to re-render `README.Rmd` every time you push. 
#An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

```
